Crystals

### 2017-06-11 doc/ms.tex
Fixed error in center of mass equation
MOre verbosity

\section{Bayesian inference}
In the Bayesian framework, probability distributions are used to model
states of uncertainty about the values of unknown quantities.
Typically, one starts with the ``prior distribution''
for unknown quantities (`parameters') $\params$, written $p(\params | \info)$
(the probability distribution for $\params$ {\em given} prior information
$\info$). This is supplemented with $p(\data | \params, \info)$,
which describes the uncertainty about the data which we {\em would} have,
if we knew the parameters (and the prior information), as a function of
the parameters.

The
product of these is the joint prior
\begin{align}
p(\params, \data | \info) &= p(\params | \info)p(\data | \params, \info).
\end{align}
Once a specific observed dataset $\data_o$ is known, knowledge about
$\params$ is updated from the prior to the posterior
\begin{align}
p(\params | \data_0, \info) &\propto
    p(\params | \info)p(\data_o | \params, \info).
\end{align}
which takes the specific data $\data_0$ into account.

@@

We compute the posterior distribution for the unknown parameters of the
components, using \citep{dnest4} to generate samples from that posterior
distribution. The output is a collection of plausible values of the
parameters which can be used to approximate posterior probabilities.
For example, the probability some parameter $\theta$ is greater than 3.4
is approximately the proportion of the posterior samples that have
$\theta > 3.4$.

@@

Defining the normalised version of the wide component as
\begin{align}
g(\x) &= \frac{f_{\rm wide}(\x)}
             {\int_{-\infty}^\infty f_{\rm wide}(\x') \, d\x'},
\end{align}
its center of mass by
\begin{align}
\textnormal{center} &= \int_{-\infty}^\infty g(\x) \, d\x,
\end{align}
and its width (second central moment) by
\begin{align}
\textnormal{width} &= \sqrt{\int_{-\infty}^\infty
                            g(\x) \left(\x - \textnormal{center}\right)^2
                            \, d\x},
\end{align}
the skewness is
\begin{align}
\textnormal{skewness} &= \int_{-\infty}^\infty
                           g(\x) 
                           \left(
                             \frac{x - \textnormal{center}}{\textnormal{width}}
                           \right)^3
                         \, d\x.
\end{align}

>>>>

\section{Bayesian inference}
In the Bayesian framework
\citep{gregory2005bayesian, o2004kendall, sivia2006data},
probability distributions are used to model
states of uncertainty about the values of unknown quantities.
Typically, one starts with the ``prior distribution''
for unknown quantities (`parameters') $\params$, written $p(\params | \info)$
(the probability distribution for $\params$ {\em given} prior information
$\info$). This is supplemented with $p(\data | \params, \info)$,
which describes the uncertainty about the data which we {\em would} have,
if we knew the parameters (and the prior information), as a function of
the parameters. This describes uncertainty about what data will be observed,
but knowledge about the fact that the data has something to do with the
parameters $\params$.
The
product of these two distributions is the joint prior
\begin{align}
p(\params, \data | \info) &= p(\params | \info)p(\data | \params, \info)
\end{align}
which describes uncertainty about the value of both the parameters and the
dataset.

Once a specific observed dataset $\data_o$ is known, knowledge about
$\params$ is updated from the prior to the posterior
\begin{align}
p(\params | \data_0, \info) &\propto
    p(\params | \info)p(\data_o | \params, \info).
\end{align}
which takes the specific data $\data_0$ into account. With a specific dataset
$\data_0$ being specified, $p(\data_o | \params,\info)$ is a function of the
unknown parameters $\params$ and is called the {\em likelihood function}.
The posterior distribution is therefore proportional to the prior distribution
times the likelihood function.

When $\params$ is a large collection of parameters, the posterior distribution
is a probability distribution over a high-dimensional parameter space. To
represent it computationally, Markov Chain Monte Carlo (MCMC) methods are
often used to generate samples from the parameter space, according to the
posterior distribution. The output is a collection of plausible values of the
parameters which can be used to approximate posterior probabilities.
For example, the probability some parameter $\theta$ is greater than 3.4
is approximately the proportion of the posterior samples that have
$\theta > 3.4$.

We compute the posterior distribution for the unknown parameters of the
components, using \citep{dnest4} to generate samples from that posterior
distribution.

@@

@@

Defining the normalised version of the wide component as
\begin{align}
g(\x) &= \frac{f_{\rm wide}(\x)}
             {\int_{-\infty}^\infty f_{\rm wide}(\x') \, d\x'},
\end{align}
its center of mass by
\begin{align}
\textnormal{center} &= \int_{-\infty}^\infty x g(\x) \, d\x,
\end{align}
and its width (second central moment) by
\begin{align}
\textnormal{width} &= \sqrt{\int_{-\infty}^\infty
                            g(\x) \left(\x - \textnormal{center}\right)^2
                            \, d\x},
\end{align}
the skewness is
\begin{align}
\textnormal{skewness} &= \int_{-\infty}^\infty
                           g(\x) 
                           \left(
                             \frac{x - \textnormal{center}}{\textnormal{width}}
                           \right)^3
                         \, d\x.
\end{align}
